Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-06-16 MUSES_vs_BYOD_solutions.tex
Sentence not clear, stated by reviewer 4, may be related to #29
Re-writing to avoid parentheses, related to #39

The way how users have used their devices has changed in the past few years, even the number of different devices per user is increasing because of the so-called Internet of Things \cite{weber2010internet}. Thanks to it, users have more flexibility, and also at their works, because now they can use their devices to access company assets and continue working outside of the workplace. To allow this way of working is what has been called called the Bring Your Own Device (BYOD) philosophy.

@@

In this scenario several solutions have appeared in order to manage corporate security. Most of the solutions are focused for both smartphones and desktop PCs, although some are implemented for a certain platform. However, almost all of them try to be non-intrusive (regarding the users' personal data), friendly and easy to use.

>>>>

The way how users have used their devices has changed in the past few years, even the number of different devices per user is increasing because of the so-called Internet of Things \cite{weber2010internet}. Thanks to it, users have more flexibility, and also at their works, because now they can use their devices to access company assets and continue working outside of the workplace. To allow this way of working, companies started to adopt what has been called the Bring Your Own Device (BYOD) philosophy.

@@

In this scenario several solutions have appeared in order to manage corporate security. Most of the solutions are focused for both smartphones and desktop PCs, although some are implemented for a certain platform. However, almost all of them try to be non-intrusive -with regard to users' personal data-, friendly, and easy to use.
